\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-11-03 metatheory-condensed.tex
Formatting Inheritance Example.

>>>>

  \begin{lstlisting}
  Family STLC_bool extends STLC.

   FInductive ty += ty_bool
   FInductive tm += tm_true ..

   FRecursion subst
     (* Inherits all others *)

     Case tm_true ...

   End subst

   Inherit t1

  i₀ = inh-id : Inh ⋅ {} {} 
  i₁ = inh-ov i₀ (W τ₁') : Inh ⋅ {ty : 𝕊(W τ₁)} {ty : 𝕊(W τ₁')}
  s₂' : {ty : 𝕊(W τ₁')} | [ty : 𝕌] 
  i₂ = inh-ov i₁ (W τ₂') 
     : Inh ⋅ {ty : 𝕊(W τ₁); tm : 𝕊(W τ₂)} {ty : 𝕊(W τ₁'); tm : 𝕊(W τ₂') }
  (* recall s₃₁ : {ty : 𝕊(W τ₁); tm : 𝕊(W τ₂)} 
                | [ty : 𝕌;  ..] *)
  s₃₁' : {ty : 𝕊(W τ₁'); tm : 𝕊(W τ₂')} | [ty : 𝕌; ..; tm_true : tm; ..]
  ↑s₃ : Tm (⋅, [ty : 𝕌; ..; tm_true : tm; ..]) [ty : 𝕌; ..] 
  (* ↑s₃ map (the type of) s₃₁' to the sealing before extension  s₃₁ *)
  ii₃₀₀ = inh-id 
        : Inh (⋅, [ty : 𝕌; ..; tm_true : tm; ..])
              (RecSig τ₂  tm)[p₀, ↑s₃]
              (RecSig τ₂  tm)[p₀, ↑s₃]
  ii₃₀₁ = inh-extend (inh-extend ii₃₀₀ {p₁} .. ) {p₁} ..
        : Inh (⋅, [ty : 𝕌; tm :𝕌; ..; tm_true : tm; ..]) 
              (RecSig τ₂   tm)[p₀, ⇡s] (RecSig τ₂'  tm)
  i₃₁ = inh+inh i₂ ↑s₃ ii₃₀₁ : 
      Inh ⋅ {ty : 𝕊(W τ₁); ..; subst' : 𝕃(RecSig τ₂ tm)} 
            {ty : 𝕊(W τ₁'); ..; subst' : 𝕃(RecSig τ₂' tm)}
  (* s₃' : {ty : W(τ₁'); tm : W(τ₂'); subst' : 𝕃(RecSig τ₂' tm) }
          | [ty : 𝕌; .. ; tm : W(τ₂'); subst' : 𝕃(RecSig τ₂' tm)] *)
  i₃ = inh-ov i₃₁ ..
     : Inh ⋅ {ty : W(τ₁); tm : W(τ₂); subst' : 𝕃(RecSig τ₂ tm); subst : tm → nat → tm → tm}  
             {ty : W(τ₁'); tm : W(τ₂'); subst' : 𝕃(RecSig τ₂' tm); subst : subst : tm → nat → tm → tm}
  (* recall s₄ : {ty : W(τ₁); .. subst : .. } 
      | [ty : 𝕌; .. ; tm : 𝕌; .. ;subst' : 𝕃(RecSig τ₂ tm); subst : ..] *)
  s₄' : {ty : W(τ₁'); .. subst : .. } 
        | [ty : 𝕌; .. ; tm : 𝕌; .. ;subst' : 𝕃(RecSig τ₂ tm); subst : ..]
  ↑s₄ : Tm (⋅, [ty : 𝕌; .. ; tm : 𝕌; .. ; subst' : 𝕃(RecSig τ₂ tm);subst : ..]) 
          [ty : 𝕌; .. ; tm : 𝕌; .. ;subst' : 𝕃(RecSig τ₂ tm); subst : ..]
  i₄ = inh-inh i₃ ↑s₄ :
    Inh ⋅ {ty : W(τ₁); .. subst : ..; t1 : 𝕊(tm_var 0)} 
          {ty : W(τ₁'); .. subst : ..; t1 : 𝕊(tm_var 0)} 
  \end{lstlisting}

  \end{multicols}
  \end{minipage}
  \caption{Inheritance Metatheory}\label{fig:inheritance}
  \end{figure}
